04_DESeq_sexes_manipulate

### 2019-09-07 analysis/04_DESeq2_sexes_manipulate.Rmd
se false

```{r, sharedmodule}
PRL_associated <- read.csv("../results/08_PRL_associated.csv", header = T)
PRL_manipulated <- read.csv("../results/08_PRL_manipulated.csv", header = T)

>>>>

```{r, sharedmodule, fig.height= 8}
PRL_associated <- read.csv("../results/08_PRL_associated.csv", header = T)
PRL_manipulated <- read.csv("../results/08_PRL_manipulated.csv", header = T)
